---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# gamt

The goal of gamt is to ...

## Installation

You can install gamt from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("slarge/gamt")
```

## Example

Step 1. Fit GAM to answer whether temporal autocorrelation is important. Use the residuals from the gam and a log likelihood ratio test to calculate the "P.ac" value. A significant p.ac value suggests a model with autocorrelated error structure explains more of the variation in the residuals of the gam model than a model without autocorrelated error structure. Thus, using a GAMM is necessary to account for autocorrelation in the time series (i.e., use GAMM if p.ac < 0.05). If p.ac > 0.05, then GAM will be used to look for non-linearities, so this code will also fit the model and provide selection criteria (i.e. edf, GCV and AIC scores from GAM and Linear model (linear) to compare)



```{r example}
## basic example code
```
